Palomar 5 Gaps

### 2024-10-21 paper/main.tex
I'm doing it

      From the top left panel of Fig.~\ref{fig:mass_size_plane}, the immediate result is that all clusters that impact Palomar~5's stream are within a band of orbital energies from about $-2\times10^2~\textrm{km/s}^2$ to $-1\times10^2~\textrm{km/s}^2$. This is a non-surprising result indicating that in order for a cluster to perturb Palomar 5's stream, it must enter Palomar~5's orbital space. Additionally, we reproduce the results of \citet{2021MNRAS.505.5978V}, who found a wide range of possible orbital solutions for the least bound clusters, some being retrograde and some prograde. For this potential model, only 3 samplings of a globular cluster had positive energies.

      - to no surprise, you have to come within Palomar 5's orbital space

      - trying to separate to the components of the velocity, Mass, impact parameter is not fruitful. It's better just to look at the change in momentum as given in the EQ.

      - Notice that the distributions between the gap and no gap are significantly different, yet also have significant overlap. Perhaps these 3 parameters don't tell the whole story but also there's the factor identifies in Sanders, that I don't understand yet, that shows that a gap will not be identifiable.

>>>>

      From the top left panel of Fig.~\ref{fig:mass_size_plane}, the immediate result is that all clusters that impact Palomar~5's stream are within a band of orbital energies from about $-2~\textrm{ to }~-1 \times10^5~\textrm{km}^2\textrm{s}^{-2}$. This is non-surprising result indicates that in order for a cluster to perturb Palomar 5's stream, it must enter Palomar~5's orbital space. Additionally, we reproduce the results of \citet{2021MNRAS.505.5978V}, who found a wide range of possible orbital solutions for the least bound clusters, some being retrograde and some prograde. For this potential model, only 3 samplings of a globular cluster had positive energies.

      From the top left panel of Fig.~\ref{fig:mass_size_plane} shows the mass-size plane of the perturbers against those that do not provoke gaps. We find a lower limit of under $10^5~\textrm{M}_{\odot}$ for provoking gaps. Mass and size are not the full picture, since provoking a gap is given by how much momentum is injected into the stream by Eq.~\ref{eq:change_in_momentum}. However, this emperical lower limit is a practical result since the relative velocity and impact parameter are known values since they happen so long ago in the past. The bottom left panel shows a result which is more true to the nature of the physics of the problem. By tracking the closest approaches and inspecting their approximate imparted momentum, we find that the gap-creating impacts have systematically higher imparted momenta that those that do not create gaps. However, there is significant overlap. Of course, the three parameter law from ~\ref{eq:change_in_momentum} is a simplified image. \citet{2015MNRAS.450.1136E} extended this to include the characterisitc size of the perturber and separated the relative velocity into perpendicular and parallel components to the stream an subsequently quantified how the parameters effect gap evolution. However, when studying the impact geometry at this level we found no satisfying combination of the parameters that clearly discriminated between the gap and no gap case. An extension this is shown in Fig.~\ref{fig:impact_geometry_statistics}, the only additional insights being that there is an observed maximum impact parameter which is about ~100~parsecs. This is roughly on the order of magnitude of the stream width. Additionally, as \citet{2016MNRAS.457.3817S} demonstrated, the dispersion of the action-frequencies of the star-particles being impacted plays an important factor. Stream regions that are well separated by orbital frequency accept gaps easier while the regions of the stream that have a wide range of frequencies (those closests to the cluster) erase the history of the impact easier. In essence, an additional criteria is that the imparted change in frequency must be greater than the range in frequencies present in the stream area being hit.
